# | Create a Protocol
**Created:** 2019-10-16 

Wanna share a cool protocol with your lab mates in this bookdown document? Follow this guide to learn how! 

First, you'll need to clone this repository using Git in your terminal. 
```{bash, eval=FALSE}
#change directories to a desirable location
cd ~/Desktop
git clone https://github.com/OsburnLab/Protocols
```

Next, open the bookdown-demo.Rproj file in RStudio. Then, select File > New File > R Markdown...

Give this file a name in the format 'number-name.Rmd', where number is in sequential order with the other .Rmd files.

Add an H1 element chapter title to the file.
```{r, eval=FALSE}
# | Chapter Title
```

Next, add some paragraph content below this.
```{r, eval=FALSE}
# | Chapter Title
Here is some paragraph content.
```

To add a code chunk, equations, or figures, check out this [link](https://bookdown.org/yihui/bookdown/components.html).

When you're done editing the R markdown file, render the book.
```{r, eval=FALSE}
bookdown::render_book("index.rmd", "bookdown::gitbook")
```

Now it's time to update your changes online!
```{bash, eval=FALSE}
#change directories to the protocols folder
cd ~/Desktop/Protocols

#add all new files you created
git add.

#commit all of your changes and add a short description about your update
git commit -a -m "short description here"

#push your changes to the github server
git push

#update the rendered html file on the github-hosted page
cd _book
git add .
git commit -a -m "short description here"
git push
```

